---
title: "Brisabne investors In Inner Ring Houses"
author: "Jay Blake - Place Projects"
date: "November 28, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries

library(dplyr)
library(tidyr)
library(stringr)
library(kableExtra)
library(geosphere)
library(dygraphs)
library(xts)
library(ggplot2)
library(sf)
library(gganimate)
library(ggmap)
library(ggthemes)
library(lubridate)
library(stringr)
library(plotly)
library(tmap)
library(leaflet)


key<-"AIzaSyCc8qDD_PMFHTQkZb3Pm0sykFqqIXAnX0s" # Set API Key
register_google(key = key)

```

# Abstract

# Introduction

# Data

```{r Loading and Cleaning Sales Data, include=FALSE}
#Load Data
house_data <- read.csv("10 Year House Sales Data Inner Brisbane to September 2018.csv", header = TRUE, sep = ",")

# Change variable classes
house_data1 <- house_data %>%
  mutate(Geocode.Address = as.character(Geocode.Address)) %>%
  mutate(Postcode = as.factor(Postcode)) %>%
  mutate(Legal.Description = as.character(Legal.Description)) %>%
  mutate(Vendor.Address = as.character(Vendor.Address)) %>%
  mutate(Purchaser.Address = as.character(Purchaser.Address)) %>%
  mutate(Sale.Price = gsub("[$]", "", Sale.Price)) %>%
  mutate(Sale.Date = as.Date(Sale.Date, format = "%d/%m/%Y")) %>%
  mutate(Area = as.integer(Area)) %>%
  mutate(Bedrooms = as.factor(Bedrooms)) %>%
  mutate(Bathrooms = as.factor(Bathrooms)) %>%
  mutate(Car.Parks = as.integer(Car.Parks)) %>%
  mutate(X6.month.Period = as.ordered(X6.month.Period)) 

# Further data manipulation
house_data1 <- house_data1 %>%
  mutate(Sale.Price = as.integer(gsub("[,]", "", Sale.Price))) %>%
  select(1:2,7:8,11,13,15:23)

# Set variable names
names(house_data1) <- c("Entry_ID", "Geo_Address", "Suburb", "Postcode", "V_Address", "P_Address", "Price", "Date", "Area", "Bed", "Bath", "Car", "Period", "Status", "Buyer_Country")

```

```{r Table of Sales Data Data Set, echo=FALSE}

# vector of variable names
variable_names <- c("Entry ID", "Geocode Address", "Street Display", "Unit Number", "Street Number", "Street Name", "Suburb", "Postcode", "Lot Number", "Vendor Name", "Vendor Address", "Buyer Name", "Buyer Address", "Days to Sell", "Sale Price", "Sale Date", "Area", "Number of Bedrooms", "Number of Bathrooms", "Number of Carspaces", "Six Month Period", "Property Status", "Buyer Country")

# vector of variable types
Variable_type <- c("Character String", "Character String", "Character String", "Numeric Integer", "Numeric Integer", "Character String", "Unordered Factor", "Unordered Factor", "Character String", "Character String", "Character String", "Character String", "Character String", "Numeric Integer", "Numeric Integer", "Date", "Numeric Integer", "Unordered Factor", "Unordered Factor", "Unordered Factor", "Ordered Factor", "Unordered Factor", "Unordered Factor")

# Vector of variable descriptions
variable_description <- c("Unique ID of Sale", "Address for Geocoding", "Street Name and Number", "Unit Number (N/A for this data)", "House - Number in Street", "House - Name of Street", "House - Suburb", " House - Postcode", "House - Land Lot Number", "House Owner Name", "House Owner Address at Sale", "House Purchaser Name", "House Purchaser Address at Time of Contract/Settlement", "Days the House was Advertised Before Sold", "House - Sale Price", "Date of Contract Signing and Acceptance", "Land Size", "Number of Bedrooms in the House", "Number of Bathrooms in the House", "Number of Carspaces at the House Residence", "The Six Month Period Ending Date For Sale Date", "First or Subsequent Sale of the House", "Country of Residence at Sale Date of the Buyer" )

# combine vectors for table
sales_data_variable_table <- as.data.frame(cbind(variable_names, Variable_type, variable_description))

# Set Table Names
names(sales_data_variable_table) <- c("Variable Name", "Variable Type", "Variable Description")

kable(sales_data_variable_table) %>%
  kable_styling()

```

```{r Loading and Cleaning Buyer Address Coordinates, include=FALSE}

# Load data
Buyer_Addresses <- read.csv("Geocoded House Buyer Address 10 Years to September 2018.csv", sep = ",", header = TRUE)

# Change classes
Buyer_Addresses1 <- Buyer_Addresses %>%
  mutate(Purchaser.Address = as.character(Purchaser.Address))

# Set names
names(Buyer_Addresses1) <- c("Buyer_Address", "B_Lat", "B_Lon")
glimpse(Buyer_Addresses)
```

```{r Table of Geocoded Buyer Address Data Set, echo=FALSE}

variable_names1 <- c("Purchaser Address", "Latitude", "Longtitute")
Variable_type1 <- c("Character String", "Numeric Double", "Numeric Double")
variable_description1 <- c("Address of the investor at sale date", "Mapping coordinate", "Mapping coordinate")

table2 <- as.data.frame(cbind(variable_names1, Variable_type1, variable_description1))

names(table2) <- c("Variable Names", "Variable Types", "Variable Description")

kable(table2) %>%
  kable_styling()

```

```{r Loading and Cleaning House Address Coordinates, include=FALSE}

# Load data
House_Address <- read.csv("House Property Geocoded Addresses Inner Ring 10 Years to September 2018.csv", sep = ",", header = TRUE)

# Change classes
House_Addresses1 <- House_Address %>%
  mutate(Address.to.Geocode = as.character(Address.to.Geocode)) %>%
  mutate(Geocoded.Address = as.character(Geocoded.Address)) %>%
  select(1,3,2)

# Set names
names(House_Addresses1) <- c("House_Address", "H_Lat", "H_Lon")

```

```{r House Address Data Set Description, echo=FALSE}

variable_names2 <- c("House Address", "Latitude", "Longtitute")
Variable_type2 <- c("Character String", "Numeric Double", "Numeric Double")
variable_description2 <- c("Address of the house that is sold", "Mapping coordinate", "Mapping coordinate")

table3 <- as.data.frame(cbind(variable_names2, Variable_type2, variable_description2))

names(table3) <- c("Variable Names", "Variable Types", "Variable Description")

kable(table3) %>%
  kable_styling()

```

```{r Loading BrisbaneLGA Postcodes and table description, include=FALSE}

# Load postcode data
postcodes <- read.csv("BrisbaneLGA Postcodes.csv", sep = ",", header = TRUE) %>%
  mutate(Post.Code = as.factor(Post.Code))

variable_names3 <- "Postcode"
Variable_type3 <- "Unordered Factor"
variable_description3 <- "4 Digit postcodes for all suburbs within 20km of the Brisbane CBD"

table4 <- as.data.frame(cbind(variable_names3, Variable_type3, variable_description3))

names(table4) <- c("Variable Names", "Variable Types", "Variable Description") 

kable(table4) %>%
  kable_styling()


```

```{r Load Australian SA2 Polygons, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# Load polygons | two files because too large
 Mainland_Polygons <- read.csv("Australia Mainland SA2 Polygons.csv", sep = ",", header = TRUE)
 Tas_Polygons <- read.csv("Tasmania SA2 Polygons.csv", sep = ",", header = TRUE)

# make both files the same headers

 names <- c("GCCSA_Code", "GCCSA_Name", "Lat", "Lon", "PointID", "PolygonID", "SA2_FDCode", "SA2_Main_Code", "SA2_Name", "SA3_Code", "SA3_Name", "SA4_Code", "SA4_Name", "State_Code", "State_Name", "Type", "Number_of_Records")

 names(Mainland_Polygons) <- names
 names(Tas_Polygons) <- names

 # join files
 Aus_Sa2_Polygons <- rbind(Mainland_Polygons, Tas_Polygons)

# Load brisbane polygons
brisbane_polygons <- read.csv("Brisbane_Polygons.csv", sep = ",", header = TRUE)

# set names
names(brisbane_polygons) <- c("SA2_Name", "Lat", "Lon", "Point_ID", "No_Investors")
```

```{r Polygon SA2 Data Set Description}

variable_names4 <- c("SA2 Name", "Latitude", "Longtitude", "Point ID")
Variable_type4 <- c("Unordered Factor", "Numeric Double", "Numeric Double", "Numeric Integer")
variable_description4 <- c("Government Stipulated SA2 Area", "Mapping coordinate", "Mapping coordinate", "Path Order Number for Polygon Drawing")

table5 <- as.data.frame(cbind(variable_names4, Variable_type4, variable_description4))

names(table5) <- c("Variable Names", "Variable Types", "Variable Description") 

kable(table5) %>%
  kable_styling()

```

```{r Load BrisbaneLGA SA2 Names}

# Load brisbane SA2 Names
Bris_SA2_List <- read.csv("Brisbane_LGA_SA2_Names.csv", sep = ",", header = TRUE)

# set classes
Bris_SA2_List$Post.Code <- as.factor(Bris_SA2_List$PostCode)

# Load suburb sales for house_data_5
entry_hd5 <- read.csv("Entry_Suburb_HD5.csv", sep = ",", header = TRUE)
```

```{r Brisabane SA2 Area Dataset Description, echo=FALSE}

variable_names5 <- c("Suburb Name", "SA2 Name", "Postcode")
Variable_type5 <- c("Unordered Factor", "Unordered Factor", "Unordered Factor")
variable_description5 <- c("Brisbane LGA Suburb Name", "Corresponding SA2 Name", "Corresponding Postcode")

table6 <- as.data.frame(cbind(variable_names5, Variable_type5, variable_description5))

names(table6) <- c("Variable Names", "Variable Types", "Variable Description") 

kable(table6) %>%
  kable_styling()


```

```{r Load Median Price by Period, Suburb and Type Summar, include=FALSE}

# Load median summary data
median_summary <- read.csv("Suburb_Summary.csv", sep = ",", header = TRUE)

# change period to ordered factor
median_summary <- median_summary %>%
  mutate(X6.Month.Period = as.ordered(X6.Month.Period)) 

# set variable names
names(median_summary) <- c("Ring", "Period", "Type", "Suburb", "Price", "Number")


```


# Methodology

1. extract state from buyer address

```{r Extract State, include=FALSE}
# Extract State and overseas buyers 
house_data1 <- house_data1 %>%
  mutate(P_Location = ifelse(str_detect(P_Address, "QLD") & Buyer_Country == "Australia", "QLD", 
                  ifelse(str_detect(P_Address, "NSW") & Buyer_Country == "Australia", "NSW",
                    ifelse(str_detect(P_Address, "NT") & Buyer_Country == "Australia", "NT",
                      ifelse(str_detect(P_Address, "VIC") & Buyer_Country == "Australia", "VIC", 
                       ifelse(str_detect(P_Address, "SA") & Buyer_Country == "Australia", "SA", 
                         ifelse(str_detect(P_Address, "WA") & Buyer_Country == "Australia", "WA", 
                            ifelse(str_detect(P_Address, "TAS") & Buyer_Country == "Australia", "TAS",
                              ifelse(str_detect(P_Address, "ACT") & Buyer_Country == "Australia", "ACT", "OTHER"))))))))) 


```


```{r Fixing State Anomalies, include=FALSE}

# Fixing Anomolies that were found when mapping - Next time use an easier code
house_data1$P_Location[house_data1$P_Address == "7 GARNET STREET, BRUNSWICK, VIC, 3056, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "24 HOLLOWAY ROAD, BRUNSWICK, VIC, 3056, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "54 HELLER STREET, BRUNSWICK WEST, VIC, 3055, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "260 BRUNSWICK ROAD, BRUNSWICK, VIC, 3056, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "19 LYDIA STREET, BRUNSWICK, VIC, 3056, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "19 BENNIE STREET, BRUNSWICK, VIC, 3056, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "13 DANIELLA WALKWAY , BRUNSWICK EAST, VIC, 3057, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "13 DIANELLA WAY, BRUNSWICK EAST, VIC, 3057, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "4 LOWAN STREET, BRUNSWICK EAST, VIC, 3057, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "499 BLYTH STREET, BRUNSWICK EAST, VIC, 3057, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "248 STEWART STREET, BRUNSWICK, VIC, 3056, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "37 CAMBERWELL STREET, EAST VICTORIA PARK, WA, 6101, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "162 HINDMARSH ROAD, VICTOR HARBOR, SA, 5211, AUS"] <- "SA"
house_data1$P_Location[house_data1$P_Address == "51 TASMANIA CIRCLE, FORREST, ACT, 2603, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "25 PELSART STREET, RED HILL, ACT, 2603, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "21 GALMARRA STREET, NGUNNAWAL, ACT, 2913, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "10 HOWARTH PLACE, CHAPMAN, ACT, 2611, AUS"] <- "ACT"

house_data1$P_Location[house_data1$P_Address == "23 BLOODWOOD CRESCENT, DERBY, WA, 6728, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "5 GANBARR STREET, BAYNTON, WA, 6714, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "21 GROSMONT GLADE , LESCHENAULT, WA, 6233, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "45 BRINDABELLA CRESCENT, HALLS HEAD, WA, 6210, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "27 CYGNET CRESCENT, DALKEITH, WA, 6009, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "74 MILL POINT ROAD, SOUTH PERTH, WA, 6151, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "12 FANTAIL AVENUE, GWELUP, WA, 6018, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "24 ROSS AVENUE, SORRENTO, WA, 6020, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "55 ALBACORE DRIVE, SORRENTO, WA, 6020, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "31 ROMANO CRESCENT, ILUKA, WA, 6028, AUS"] <- "WA"
house_data1$P_Location[house_data1$P_Address == "64 WILLIAMS ROAD, MILLICENT, SA, 5280, AUS"] <- "SA"
house_data1$P_Location[house_data1$P_Address == "7 BUCHAN CRESCENT, FORDE, ACT, 2914, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "32 BIZANT STREET, AMAROO, ACT, 2914, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "395 ANTILL STREET, WATSON, ACT, 2602, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "87 ANTILL STREET, DOWNER, ACT, 2602, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "52 CLIANTHUS STREET, O`CONNOR, ACT, 2602, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "3 TENNYSON CRESCENT, FORREST, ACT, 2603, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "3 HACKING CRESCENT, NARRABUNDAH, ACT, 2604, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "73 MACALISTER CRESCENT, CURTIN, ACT, 2605, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "10 HOWARTH PLACE, CHAPMAN, ACT, 2611, AUS"] <- "ACT"
house_data1$P_Location[house_data1$P_Address == "48 WILSMORE CRESCENT, CHIFLEY, ACT, 2606, AUS"] <- "ACT"

house_data1$P_Location[house_data1$P_Address == "416 UNA STREET, MOUNT STUART, TAS, 7000, AUS"] <- "TAS"
house_data1$P_Location[house_data1$P_Address == "531 CREAMERY ROAD, TYNTYNDER, VIC, 3586, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "27 VALENTINE STREET, BENDIGO, VIC, 3550, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "155 THORNTONS ROAD, DIXIE, VIC, 3265, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "SCOTTS CHARTERED ACCOUNTANTS410 PAKINGTON STREET, NEWTOWN, VIC, 3220, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "11 VIEWBANK COURT, POINT COOK, VIC, 3030, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "9 AUSTEN CRESCENT, YARRAVILLE, VIC, 3013, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "38 MERCANTILE PARADE, KENSINGTON, VIC, 3031, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "62 CONVENTY STREET, SOUTHBANK, VIC, 3006, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "137 CANTERBURY ROAD, MIDDLE PARK, VIC, 3206, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "33 HINTON LANE, PRAHRAN, VIC, 3181, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "29 GLEN HUNTLY ROAD, ELWOOD, VIC, 3184, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "29 WIDDOP CRESCENT, HAMPTON EAST, VIC, 3188, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "45 HENTY STREET, RESERVOIR, VIC, 3073, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "6 ADVANTAGE DRIVE, DANDENONG SOUTH, VIC, 3164, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "6 ADVANTAGE DRIVE, DANDENONG SOUTH, VIC, 3175, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "12 TARUNA RISE, MONTROSE, VIC, 3765, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "1488 FERNTREE GULLY ROAD, KNOXFIELD, VIC, 3180, AUS"] <- "VIC"

house_data1$P_Location[house_data1$P_Address == "15 ANTIBES ST, PARKDALE, VIC, 3195, AUSTRALIA"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "1A LEIGH STREET, BENTLEIGH EAST, VIC, 3165, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "46 AMBRIE CRESCENT, NOBLE PARK, VIC, 3174, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "15 GLENVALE CRESCENT, MULGRAVE, VIC, 3170, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "3 TETRAGONA QUADRANT , ROWVILLE, VIC, 3178, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "113 JENOLA PARADE, WANTIRNA SOUTH, VIC, 3152, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "18 BATES AVENUE, UPPER FERNTREE GULLY, VIC, 3156, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "69 STANLEY AVENUE, MOUNT WAVERLEY, VIC, 3149, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "5 MINERVA CRESCENT, VERMONT SOUTH, VIC, 3133, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "2 MINDAH COURT, VERMONT SOUTH, VIC, 3133, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "7 IAN CRESCENT, MITCHAM, VIC, 3132, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "110 WINDSOR CRESCENT, SURREY HILLS, VIC, 3127, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "1 KINOCH AVENUE, MONT ALBERT, VIC, 3127, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "31 CLEVELAND AVENUE, LOWER PLENTY, VIC, 3093, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "70 MAUNT STREET, HEIDELBERG, VIC, 3084, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "483 PLENTY ROAD, PRESTON, VIC, 3072, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "18 ROTHSCHILD STREET, GLEN HUNTLY, VIC, 3163, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "1 BEATTY CRESCENT, ORMOND, VIC, 3204, AUS"] <- "VIC"
house_data1$P_Location[house_data1$P_Address == "16 RUBENS GROVE, CANTERBURY, VIC, 3126, AUS"] <- "VIC"


```

 Determine Investor

```{r Determining Investors, include=FALSE}

# Join Coordinates

House_Data1_Wcoords <- left_join(house_data1, House_Addresses1, by = c("Geo_Address" = "House_Address"))
House_Data1_Wcoords <- left_join(House_Data1_Wcoords, Buyer_Addresses1, by = c("P_Address" = "Buyer_Address"))

# Create DF
Distance_Dataframe <- House_Data1_Wcoords %>%
  select(1,17:20)

# Calculate Distance as new variable
Distance_Dataframe <- Distance_Dataframe %>% rowwise() %>% 
           mutate(Distance = round(distHaversine(c(H_Lon, H_Lat), c(B_Lon, B_Lat))/1000,3))
                  
# Choose Investor|Owner Occupier <50m

Distance_Dataframe <- Distance_Dataframe %>%
  mutate(Status = ifelse(Distance <0.050, "Owner Occupier", "Investor"))

# Join distance and status to main dataframe 
house_data2 <- left_join(house_data1, Distance_Dataframe, by = c("Entry_ID" = "Entry_ID"))

high_cutoff <- length(Distance_Dataframe$Distance[Distance_Dataframe$Distance <0.05])
mid_cutoff <- length(Distance_Dataframe$Distance[Distance_Dataframe$Distance <0.025])
low_cutoff <- length(Distance_Dataframe$Distance[Distance_Dataframe$Distance <0.01])
length_buyers <- length(Distance_Dataframe$Distance)

```

`r high_cutoff/length_buyers`
`r mid_cutoff/length_buyers`
`r low_cutoff/length_buyers`

Determine if buyer is from Brisbane LGA 

```{r Determine BrisbaneLGA Based Buyers, include=FALSE}

# Determine Brisbane Buyers
house_data2 <- house_data2 %>%
  mutate(Buyer_Postcode = substr(sapply(strsplit(P_Address, "QLD, ", fixed = FALSE), "[",2), 1, 4)) %>% # Extract QLD postcodes
  mutate(BrisbaneLGA_Buyer = Buyer_Postcode %in% Bris_SA2_List$PostCode) %>% # Determine if Postcode is in BrisbaneLGA
  select(-c("Buyer_Postcode")) # Drop QLD buyer postcodes

```


# Results and Discussion

## 4. WHere are Buyers Coming From

### 4.1 Over the Last 10 Years

```{r Summary Table Buyer State/Overseas, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Create summary dataframe
Buyer_Macro_Location <- house_data2 %>%
  filter(Status.y == "Investor") %>%
  group_by(Buyer_Country) %>%
  summarise(Total = n()) %>%
  arrange(desc(Total))

Buyer_Macro_Location <- Buyer_Macro_Location %>%
  mutate(Proportion_Investors = paste(round(Total/sum(Total)*100, 2), "%", sep = "")) %>%
  mutate(Proportion_Total = paste(round(Total/length(house_data2$Status.y)*100, 2), "%", sep = ""))
  
# Create table 
kable(Buyer_Macro_Location, caption = "Table.1 - Investors by Location, Number and Proportion") %>%
  kable_styling()
```

```{r Summary Australian State/Territory, echo=FALSE}

Aus_state_summary <- house_data2 %>%
  filter(P_Location != "OTHER" & Status.y == "Investor") %>%
  group_by(P_Location) %>%
  summarise(Number = n()) %>%
  arrange(desc(Number))

Aus_state_summary <- Aus_state_summary %>%
  mutate(Proportion = paste(round(Number/sum(Number)*100, 2), "%", sep = "")) %>%
  mutate(Proportion_Total = paste(round(Number/length(house_data2$Status.y)*100, 2), "%", sep = ""))

kable(Aus_state_summary, caption = "Table.2 - Investors Numbers and Proportions by Australian State/Territory") %>%
  kable_styling()

```

Map of australian investors
```{r Map of Australia Investors}

# select only Australian based investors
house_data4 <- house_data2 %>%
  filter(Buyer_Country == "Australia" & Status.y == "Investor")

QLD <- house_data4 %>%
  filter(P_Location == "QLD")
NSW <- house_data4 %>%
  filter(P_Location == "NSW")
VIC <- house_data4 %>%
  filter(P_Location == "VIC")
TAS <- house_data4 %>%
  filter(P_Location == "TAS")
ACT <- house_data4 %>%
  filter(P_Location == "ACT")
SA <- house_data4 %>%
  filter(P_Location == "SA")
WA <- house_data4 %>%
  filter(P_Location == "WA")
NT <- house_data4 %>%
  filter(P_Location == "NT")

leaflet(options = leafletOptions(
  minZoom = 4, dragging = TRUE)) %>% 
  addProviderTiles("Esri") %>% 
  addCircleMarkers(data = QLD, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "red", label = ~P_Address, group = "Queensland") %>%
  addCircleMarkers(data = NSW, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "blue", label = ~P_Address, group = "New South Wales") %>%
  addCircleMarkers(data = VIC, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "green", label = ~P_Address, group = "Victoria") %>%
  addCircleMarkers(data = TAS, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "black", label = ~P_Address, group = "Tasmania") %>%
  addCircleMarkers(data = ACT, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "orange", label = ~P_Address, group = "Australian Capital Territory") %>%
  addCircleMarkers(data = SA, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "yellow", label = ~P_Address, group = "South Australia") %>%
  addCircleMarkers(data = WA, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "purple", label = ~P_Address, group = "Western Australia") %>%
  addCircleMarkers(data = NT, lng = ~B_Lon, lat = ~B_Lat, radius = 2, color = "turqoise", label = ~P_Address, group = "Northern Territory") %>%
  setView(lng = 133.775136, lat = -25.274398, zoom = 4) %>%
  addLayersControl(overlayGroups = c("Queensland", "New South Wales", "Victoria", "Tasmania", "Australian Capital Territory", "South Australia", "Western Australia", "Northern Territory"))
?addPolygons

```


```{r Investor Proportion, echo=FALSE}
# Create summary dataframe
Investor_Proportions <- house_data2 %>%
  group_by(Status.y, BrisbaneLGA_Buyer) %>%
  summarise(Total = n()) %>%
  arrange(desc(Total)) 

# Investor_Proportions | results - 3 anomolies to fix

# fix anomolies
   
house_data2$BrisbaneLGA_Buyer[house_data2$Entry_ID == "irh10016139"] <- TRUE
house_data2$BrisbaneLGA_Buyer[house_data2$Entry_ID == "irh10028920"] <- TRUE
house_data2$BrisbaneLGA_Buyer[house_data2$Entry_ID == "irh10086662"] <- TRUE

# Re-do summary dataframe
Investor_Proportions <- house_data2 %>%
  group_by(Status.y,BrisbaneLGA_Buyer) %>%
  summarise(Total = n()) %>%
  arrange(desc(Total)) 

# Add proportions
Investor_Proportions$Proportion <- paste(round(Investor_Proportions$Total/sum(Investor_Proportions$Total)*100,2),"%", sep = "")

# Create table 
kable(Investor_Proportions) %>%
  kable_styling()

```


```{r TimeSeries Bar Map Investor Locations, echo=FALSE}

# Split P_Location QLD into Brisbane and Other Queensland

house_data3 <- house_data2 %>%
  filter(Status.y == "Investor") %>%
  mutate(P_Location = ifelse(BrisbaneLGA_Buyer == TRUE, "BrisbaneLGA", P_Location))

# Create summary 
TS_IL_Summary <- house_data3 %>%
  group_by(Period, P_Location) %>%
  summarise(Number = n())

# Spread summary
TS_IL_Summary <- spread(TS_IL_Summary, P_Location, Number)

Period <- TS_IL_Summary$Period # Extract Period
Period <- paste(30, Period) # Past Day
Period <- as.Date(Period, format = "%d %Y %B") # change to date format

QLD <- TS_IL_Summary$QLD
BrisbaneLGA <- TS_IL_Summary$BrisbaneLGA
ACT <- TS_IL_Summary$ACT
NSW <- TS_IL_Summary$NSW
NT <- TS_IL_Summary$NT
SA <- TS_IL_Summary$SA
TAS <- TS_IL_Summary$TAS
VIC <- TS_IL_Summary$VIC
WA <- TS_IL_Summary$WA
OTHER <- TS_IL_Summary$OTHER
class(BrisbaneLGA)
# Combine vectors
TS_IL2 <- cbind(BrisbaneLGA, QLD, NSW, VIC, SA, WA, TAS, NT, ACT, OTHER)
# Remove NAs and replace with 0s
TS_IL2[is.na(TS_IL2)] <- 0

# Convert data to time series
TS_IL3 <- xts(TS_IL2, Period,  frequency = 2)

# Plot data on time series graph
dygraph(TS_IL3, "The Investor Market is Declining in the Inner Brisbane House Market") %>%
  dyStackedBarGroup(c('OTHER', 'ACT', 'NT', 'SA', 'WA', 'TAS', 'VIC', 'NSW', 'QLD', 'BrisbaneLGA')) %>% # Add order of Stacked Bars
  dyAxis("y", label = "Nunber of Investor")
 

```


### 4.2 Brisbane LGA

Heat Map of Brisbane

```{r Make Circles 5km in Maps, include=FALSE}

# 8 Circle example at 450m


data = data.frame(
  ID = as.numeric(c(1:1)), # number of points and there coordinates below
  longitude = as.numeric(c(153.025124)),
  latitude = as.numeric(c(-27.469771))
)

#################################################################################
# create circles data frame from the centers data frame
make_circles <- function(centers, radius, nPoints = 100){
  # centers: the data frame of centers with ID
  # radius: radius measured in kilometer
  #
  meanLat <- mean(centers$latitude)
  # length per longitude changes with lattitude, so need correction
  radiusLon <- radius /111 / cos(meanLat/57.3) 
  radiusLat <- radius / 111
  circleDF <- data.frame(ID = rep(centers$ID, each = nPoints))
  angle <- seq(0,2*pi,length.out = nPoints)
  
  circleDF$lon <- unlist(lapply(centers$longitude, function(x) x + radiusLon * cos(angle)))
  circleDF$lat <- unlist(lapply(centers$latitude, function(x) x + radiusLat * sin(angle)))
  return(circleDF)
}

# here is the data frame for all circles
myCircles5 <- make_circles(data, 5) # this is in km therefore 0.45 is 450m

```


```{r Make Circles 10km in Maps, include=FALSE}

# 8 Circle example at 450m


data = data.frame(
  ID = as.numeric(c(1:1)), # number of points and there coordinates below
  longitude = as.numeric(c(153.025124)),
  latitude = as.numeric(c(-27.469771))
)

myCircles10 <- make_circles(data, 10) # this is in km therefore 0.45 is 450m
```


```{r Make Circles 20km in Maps, include=FALSE}

# 8 Circle example at 450m


data = data.frame(
  ID = as.numeric(c(1:1)), # number of points and there coordinates below
  longitude = as.numeric(c(153.025124)),
  latitude = as.numeric(c(-27.469771))
)

# here is the data frame for all circles
myCircles20 <- make_circles(data, 20) # this is in km therefore 0.45 is 450m
```


```{r}

brisbane_spatial_polys_df %>%
  leaflet(options = leafletOptions(dragging = TRUE)) %>%
  addProviderTiles("Esri") %>%
  addPolygons(weight = 1, color = "red", group = "SA2 Area Density",
              # highlight polygons on hover
              highlight = highlightOptions(weight = 5, color = "white",
                                           bringToFront = TRUE)) %>%
 setView(lng = 153.025124, lat = -27.469771, zoom = 10) %>%
addCircleMarkers(data = QLD, lng = ~B_Lon, lat = ~B_Lat, radius = 1, color = "blue", label = ~P_Address, group = "Investor Locations") %>%
  addLayersControl(overlayGroups = c("Investor Locations", "SA2 Area Density"))

```



```{r Brisbane Heat Map, echo=FALSE}

# left join suburb data for investors
house_data5 <- left_join(house_data2, entry_hd5, by = c("Entry_ID" = "Entry_ID")) 

# filter data to BrisbaneLGA investors
house_data6 <- house_data5 %>%
  filter(Status.y == "Investor") %>%
  filter(Buyer_Country == "Australia") %>%
  filter(Suburb.y %in% Bris_SA2_List$SuburbName) 
  
# Join SA2 names for investor suburbs
house_data7 <- left_join(house_data6, Bris_SA2_List, by = c("Suburb.y" = "SuburbName"))

# Get Brisbane Coordinates
  brisbane <- c(lon = 153.025124, lat = -27.469771)
  
# Get Brisbane Map  
brisbane_map <- get_map(location = brisbane, zoom = 11, scale = 1)
glimpse(brisbane_polygons)

# create Polygon map of brisbane buyers
ggmap(brisbane_map) +                                               # initialize ggplot object
  geom_polygon(data = brisbane_polygons, aes(x = Lon, 
                                             y = Lat, 
                                             group = SA2_Name, 
                                             fill = cut_number(No_Investors, 9)),
                                             alpha = 0.8) +               
  scale_fill_brewer("No. Investors Range", palette = "OrRd") + # fill with brewer colors 
  ggtitle("Brisbane Investors of Inner Brisbane Houses") +
  theme(line = element_blank(),                          # remove axis lines .. 
        axis.text=element_blank(),                       # .. tickmarks..
        axis.title=element_blank(),                      # .. axis labels..
        panel.background = element_blank()) +            # .. background gridlines
  coord_equal()                                          # set coordinate system
 

```



```{r Brisbane Point Map With Circles, echo=FALSE}

# set create distance matrix from brisbane centre

Distance_Dataframe2 <- house_data7 %>%
  select(1,19:20)

# Calculate Distance as new variable
Distance_Dataframe2 <- Distance_Dataframe2 %>% rowwise() %>% 
  mutate(Distance_FBrisbane = round(distHaversine(c(153.025124, -27.469771), c(B_Lon, B_Lat))/1000,3)) %>%
  select(1,4)
  
# join distance from brisbane back to the house data
house_data8 <- left_join(house_data7, Distance_Dataframe2, by = c("Entry_ID" = "Entry_ID"))

# create classification for distance from brisbane
house_data8 <- house_data8 %>%
  mutate(ring_classification = ifelse(Distance_FBrisbane <= 5, "5km",
                                      ifelse(Distance_FBrisbane > 5 & Distance_FBrisbane <= 10, "10km",
                                             ifelse(Distance_FBrisbane >10 & Distance_FBrisbane <= 20, "20km", "More Than 20km"))))

# create map with points and rings
ggmap(brisbane_map) +                                               # initialize ggplot object
  geom_point(data = house_data8, aes(x = B_Lon, 
                                    y = B_Lat, group = ring_classification,
                                    color = ring_classification), size = 0.7) +
  scale_fill_brewer("No. Investors Range", palette = "OrRd") + # fill with brewer colors 
  ggtitle("Brisbane Investors of Inner Brisbane Houses") +
  theme(line = element_blank(),                          # remove axis lines .. 
        axis.text=element_blank(),                       # .. tickmarks..
        axis.title=element_blank(),                      # .. axis labels..
        panel.background = element_blank()) +            # .. background gridline
    geom_polygon(data = myCircles5, aes(lon, lat, group = ID), color = "red", alpha = 0, lwd = 1) +
    geom_polygon(data = myCircles10, aes(lon, lat, group = ID), color = "orange", alpha = 0, lwd = 1) +
    geom_polygon(data = myCircles20, aes(lon, lat, group = ID), color = "yellow", alpha = 0, lwd = 1)

 
```


```{r Summary of Buyers in Each Ring, echo=FALSE}

# summarise rings

ring_summary <- house_data8 %>%
  group_by(ring_classification) %>%
  summarise(Number = n()) %>%
  filter(ring_classification != "More Than 20km")

ring_summary <- ring_summary %>%
  mutate(proportion = paste(round(Number/sum(Number)*100,0), "%", sep = ""))


kable(ring_summary) %>%
  kable_styling()


```

```{r Where are the Investors Buying Heatmap, echo=FALSE}


# Removing space for match of SA2 Name
house_data9 <- house_data8 %>%
  mutate(Suburb.x = gsub('\\s+', '', Suburb.x)) 

# Join SA2 Name to house sale 
house_data9 <- left_join(house_data9, Bris_SA2_List, by = c("Suburb.x" = "SuburbName"))

# Creating summary for match
house_data9_summary <- house_data9 %>%
  group_by(SA2Name.y) %>%
  summarise(Number_of_Houses = n())

# filter out only polygons for Inner Brisbane houses SA2 areas
brisbane_polygons2 <- brisbane_polygons %>%
  filter(toupper(SA2_Name) %in% house_data9_summary$SA2Name.y) %>%
  mutate(SA2_Name = toupper(SA2_Name)) # create all upper case for next join

# left join summary data

brisbane_polygons2 <-  left_join(brisbane_polygons2, house_data9_summary, by = c("SA2_Name" = "SA2Name.y"))

#Get zoomed brisbane map
brisbane_map2 <- get_map(location = brisbane, zoom = 12, scale = 1)

# Create heat map of property density where investors are buying
ggmap(brisbane_map2) +                                               # initialize ggplot object
  geom_polygon(data = brisbane_polygons2, aes(x = Lon, 
                                             y = Lat, 
                                             group = SA2_Name, 
                                             fill = cut_number(Number_of_Houses, 9)),
                                             alpha = 0.8) +              
  scale_fill_brewer("No. Houses Range", palette = "OrRd") + # fill with brewer colors 
  ggtitle("Brisbane Houses") +
  theme(line = element_blank(),                          # remove axis lines .. 
        axis.text=element_blank(),                       # .. tickmarks..
        axis.title=element_blank(),                      # .. axis labels..
        panel.background = element_blank())             # .. background gridlines
```

```{r Summary of House Sales in Suburbs, include=FALSE}

house_data9_summary %>%
  arrange(desc(Number_of_Houses)) %>%
kable() %>%
  kable_styling()




```


```{r Distance Summary 3 Ring Buyers, echo=FALSE}
house_data9_summary2 <- house_data9 %>%
   filter(ring_classification != "More Than 20km") %>%
  group_by(ring_classification) %>%
  summarise(Average_Distance = paste(round(mean(Distance),1), "km", sep = ""))

kable(house_data9_summary2) %>%
  kable_styling()


```



```{r Bedrooms they buy and Area they buy, echo=FALSE}


house_data11 <- house_data9 %>%
  mutate(Price_Bracket = ifelse(Price < 200000, "Under $200,000",
                                ifelse(Price < 400000, "$200k to $400k",
                                       ifelse(Price < 600000, "$400k to $600k",
                                              ifelse(Price < 800000, "$600k to $800k",
                                                     ifelse(Price <1000000, "800k to $1m", "$1m Plus"))))))
  
house_data11_summary <- house_data11 %>%
  mutate(Bed = as.integer(Bed) - 1) %>%
  filter(Bed < 11) %>%
  group_by(Price_Bracket, Bed) %>%
  summarise(Number = n()) 


ggplot(house_data11_summary, aes(Bed, Price_Bracket, fill = Number)) +
  geom_tile(stat = "identity") 




```




# Conclusion











