---
title: "High Rise vs Low Rise"
author: "Place Advisory"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

library(readr)
library(dplyr)
library(geosphere)
library(ggplot2)
library(ggmap)
library(leaflet)
library(plotly)
library(xts)
library(dygraphs)
library(gridExtra)
library(scales)

```

```{r Load Data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# Load sales data
sales_data <- read_csv("R:/Projects/Market Analysis and Database Records/Sales Data/Sales Data CSV Files/All_Sales_Data.csv")

# Load Building List
building_list <- read_csv("R:/Projects/Jay/Jay Portfolio/SQL Projects/Sales Data Database/Buildings.csv")

# Load Resales Data
resales <- read_csv("R:/Projects/Jay/Jay Portfolio/SQL Projects/Sales Data Database/Resales.csv")

# Clean resales
resales_cleaned <- resales %>%
  mutate(Resale = as.factor(Resale))

```

```{r Clean and Mutate Dataframes, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

#change classes of sales data variables drop unwanted variables and filter to last 10 years
sales_data_cleaned <- sales_data %>%
  mutate(Suburb = as.factor(Suburb)) %>%
  mutate(Postcode = as.factor(Postcode)) %>%
  mutate(Property_Type = as.factor(Property_Type)) %>%
  mutate(Sale_Date = as.Date(Sale_Date, format = "%m/%d/%Y")) %>%
  mutate(No_Beds = as.factor(No_Beds)) %>%
  mutate(No_Baths = as.factor(No_Baths)) %>%
  mutate(No_Carparks = as.factor(No_Carparks)) %>%
  mutate(Six_Month_Period_Mar_Sep = as.ordered(Six_Month_Period_Mar_Sep)) %>%
  mutate(Region = as.factor(Region)) %>%
  mutate(Waterfront = as.factor(Waterfront)) %>%
  select(1:2, 7:11, 16:24) %>%
  filter(Property_Type == "Apartments" | Property_Type == "Townhouses") 


# change classes of building data variables and drop unwanted variables

buildings_cleaned <- building_list %>%
  mutate(Building_Type = as.factor(Building_Type)) %>%
  mutate(Suburb = as.factor(Suburb)) %>%
  mutate(`Waterfront/nWaterfront` = as.factor(`Waterfront/nWaterfront`)) %>%
  mutate(Scale = as.factor(Scale)) %>%
  select(1:2, 8:10)
  

```

```{r Select only properties within 5km of Brisbane CBD, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# merge coordinates to sales data

sales_data_merge <- left_join(sales_data_cleaned, buildings_cleaned, by = c("Building_Lot_Number" = "Plan_Number"))

sales_data_merge <- sales_data_merge %>% rowwise() %>%
    mutate(Distance = round(distHaversine(c(Longitude, Latitude), c(153.025124, -27.469771))/1000,3)) # static Brisbane coordinates for formula
  
### drop any buildings outside 5km
sales_data_merge <- sales_data_merge %>%
  filter(Distance <= 5)
  

```

```{r Make 1:5km ring Polygons, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

data = data.frame(
  ID = as.numeric(c(1)), # number of points and there coordinates below
  longitude = as.numeric(c(153.025124)),
  latitude = as.numeric(c(-27.469771))
  )

# create circles data frame from the centers data frame
make_circles <- function(centers, radius, nPoints = 1000){
  # centers: the data frame of centers with ID
  # radius: radius measured in kilometer
  #
  meanLat <- mean(centers$latitude)
  # length per longitude changes with lattitude, so need correction
  radiusLon <- radius /111 / cos(meanLat/57.3) 
  radiusLat <- radius / 111
  circleDF <- data.frame(ID = rep(centers$ID, each = nPoints))
  angle <- seq(0,2*pi,length.out = nPoints)
  
  circleDF$lon <- unlist(lapply(centers$longitude, function(x) x + radiusLon * cos(angle)))
  circleDF$lat <- unlist(lapply(centers$latitude, function(x) x + radiusLat * sin(angle)))
  return(circleDF)
}

# here is the data frame for all circles
myCircles1 <- make_circles(data, 1) # 1km
myCircles2 <- make_circles(data, 2) # 2km
myCircles3 <- make_circles(data, 3) # 3km
myCircles4 <- make_circles(data, 4) # 4km
myCircles5 <- make_circles(data, 5) # 5km

```

As the current residential construction boom comes to the end of a cycle, Inner Brisbane has undoubtedly seen a transformation with many new buildings being added to the market. The following interactive report has broken down each segment of the Inner Brisbane market to provide a more detailed analysis of the relevant properties.

*For the purposes of this report, the following categorical breakdown for units is applied. Please click on the different tabs to get an explanation of each category.*

## CATEGORIES {.tabset .tabset-fade .tabset-pills}
### Small Size Townhouse Complexes 

These complexes contain a maximum of only 10 townhouses and account for the majority of townhouses in Inner Brisbane. These townhouse complexes are found more predominantly between 3km and 5km from Brisbane's centre to the south and east and between 2km and 4km to the north and west parts of Inner Brisbane.

### Medium Size Townhouse Complexes

These complexes contain a minimum of 11 townhouses and a maximum of 40. They account for only a small proportion of all units in Inner Brisbane and are found scattered throughout the region. 

### Low Rise Apartment Buildings

Low-Rise apartment buildings contain a maximum of 10 apartments. These buildings are the most prevalent of any category throughout the Inner Brisbane region and are found at all distances. However, the proportion of low rise apartment buildings decreases closer to the CBD. 

### Mid Rise Apartment Buildings

Mid-Rise apartment buildings contain a minimum of 11 apartments and a maximum of 40. These buildings are predominantly located between 1km and 3km to the CBD's east and between 3km and 4km to the south west.

### High Rise Apartment Buildings

High-Rise apartment buildings saw substantial development during the recent "apartment boom" in Inner Brisbane. These buildings contain at least 41 apartments and are most commonly located between Toowong heading north east across the CBD to Teneriffe. The majority of these buildings are concentrated within a 3km radius of Brisbane's centre.

## INNER BRISBANE UNITS

In the map below, all residential buildings within a 5km radius of Brisbane's centre have been plotted by type and size. Use the icon in the top right corner to filter the map output with your selected property type and radius. Please note that some recently completed buildings may not yet be visible.

&nbsp;  

```{r Leaflet Map of Buildings, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "centre", fig.width = 8}

# reduce dataframe and write it for manual unique(Building_Name) formatting due to grouping issue in R

#sales_data_merge1 <- sales_data_merge %>%
 # select(Building_Name, Latitude, Longitude, Property_Type, Scale) %>%
  #write.csv("Sales_data_merge_for_Grouping.csv")

# After Manual grouping reload the data
sales_data_merge_2 <- read.csv("R:/Projects/Jay/Jay Portfolio/R Projects/Research Blogs/HighRise vs LowRise and Best Performing Jan 2019/Sales_data_merge_for_Grouping_Unique.csv")

# create filtered dataframes for leaflet map with unique buildings

small_townhouses <- sales_data_merge_2 %>%
  filter(Property_Type == "Townhouses" & Scale == "Ten units or less") 

medium_townhouses <- sales_data_merge_2 %>%
  filter(Property_Type == "Townhouses" & Scale == "Mid sized (11 to 40 units)") 

small_apartments <- sales_data_merge_2 %>%
  filter(Property_Type == "Apartments" & Scale == "Ten units or less") 

medium_apartments <- sales_data_merge_2 %>%
  filter(Property_Type == "Apartments" & Scale == "Mid sized (11 to 40 units)") 

large_apartments <- sales_data_merge_2 %>%
  filter(Property_Type == "Apartments" & Scale == "Large scale (41 units or greater)") 

# Create Leafleat Map

Brisbane_Map <- leaflet(options = leafletOptions(dragging = TRUE, minZoom = 12)) %>% 
  addProviderTiles("Esri") %>% 
  setMaxBounds(lng1 = 152.970951, lng2 = 153.116971, lat1 = -27.410852, lat2 = -27.532954) %>%
 addCircleMarkers(data = small_townhouses, lng = ~Longitude, lat = ~Latitude, radius = 1.5, color = "turquoise", fillOpacity = 1, group = "Small Size Townhouse Complexes") %>% 
   addCircleMarkers(data = medium_townhouses, lng = ~Longitude, lat = ~Latitude, radius = 1.5, color = "steelblue", fillOpacity = 1, group = "Medium SIzed Townhouse Complexes") %>%
  addCircleMarkers(data = small_apartments, lng = ~Longitude, lat = ~Latitude, radius = 1.5, color = "violet", fillOpacity = 1, group = "Low-Rise Apartment Buildings") %>%
  addCircleMarkers(data = medium_apartments, lng = ~Longitude, lat = ~Latitude, radius = 1.5, color = "magenta", fillOpacity = 1, group = "Mid-Rise Apartment Buildings") %>%
  addCircleMarkers(data = large_apartments, lng = ~Longitude, lat = ~Latitude, radius = 1.5, color = "slateblue", fillOpacity = 1, group = "High-Rise Apartment Buildings") %>%
   addPolygons(data = myCircles1, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "1km Ring") %>%
   addPolygons(data = myCircles2, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "2km Ring") %>%
   addPolygons(data = myCircles3, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "3km Ring") %>%
   addPolygons(data = myCircles4, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "4km Ring") %>%
   addPolygons(data = myCircles5, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "5km Ring") %>%
 addLayersControl(overlayGroups = c("Small Size Townhouse Complexes", "Medium SIzed Townhouse Complexes", "Low-Rise Apartment Buildings", "Mid-Rise Apartment Buildings", "High-Rise Apartment Buildings", "1km Ring", "2km Ring", "3km Ring", "4km Ring", "5km Ring"))
                  
Brisbane_Map
```

To find out what is currently happening in the Inner Brisbane off the plan apartment market, please read our [APARTMENT REPORT](http://www.placeprojects.com.au/quarterly-reports/).

## MEDIAN PRICE BY CATEGORY

The graph below displays median price movements for each unit category over the last 10 years. Interestingly, both townhouse categories have consistently recorded higher median prices than all three apartment categories over the past 10 years. Furthermore, low-rise apartment buildings have recorded considerably lower median prices than the other four categories. This is attributable to the fact that many older apartment buildings are located further from the CBD than their counterparts. In contrast, many newer buildings that have been constructed in recent years are mid and high-rise apartment buildings which have been attracting a premium prices. 

```{r Median Price Graph, echo=FALSE, fig.align="centre", fig.height =7, fig.width = 12, message=FALSE, warning=FALSE, paged.print=FALSE}

# Select and Filter Data from 10 Year Graphs - Apartments
Ten_Years_Sales_Apartments <- sales_data_merge %>%
  filter(Six_Month_Period_Mar_Sep > "2008 September" & Six_Month_Period_Mar_Sep < "2019 March", Property_Type == "Apartments") %>%
  group_by(Six_Month_Period_Mar_Sep, Scale) %>%
  summarise(Median_Price = median(Sale_Price), No_Sales = n()) %>%
  mutate(Type = paste("Apartments ", Scale)) # ncreate second type variable 

#### Type will not split properly so the process is repeated for townhouses and then joined back together

# Select and Filter Data from 10 Year Graphs - Townhouses
Ten_Years_Sales_Townhouses <- sales_data_merge %>%
  filter(Six_Month_Period_Mar_Sep > "2008 September" & Six_Month_Period_Mar_Sep < "2019 March", Property_Type == "Townhouses") %>%
  filter(Scale != "Large scale (41 units or greater)") %>%
  group_by(Six_Month_Period_Mar_Sep, Scale) %>%
  summarise(Median_Price = median(Sale_Price), No_Sales = n()) %>%
  mutate(Type = paste("Townhouses ", Scale))

# Join data back together
Ten_Years_Sales <- rbind(Ten_Years_Sales_Apartments, Ten_Years_Sales_Townhouses) %>%
  mutate(Type = as.factor(Type)) 

# ungroup and change class
Ten_Years_Sales <-ungroup(Ten_Years_Sales) %>%
  mutate(Six_Month_Period_Mar_Sep = as.factor(Six_Month_Period_Mar_Sep))

# drop unwanted factor level for 6 month period
Ten_Years_Sales <- Ten_Years_Sales %>%
  mutate(Six_Month_Period_Mar_Sep = droplevels(Ten_Years_Sales$Six_Month_Period_Mar_Sep, exclude = if(anyNA(levels(Ten_Years_Sales$Six_Month_Period_Mar_Sep))) NULL else NA)) 

# geom_line colour vector
line_colours <- c("slateblue", "magenta", "violet", "steelblue", "turquoise")

legend_names <- c("High-Rise Apartment Buildings", "Mid-Rise Apartment Buildings", "Low-Rise Apartment Buildings", "Medium Size Townhouses Complexes",  "Small Size Townhouse Complexes")

# create ggplot line graph of median prices
(Property_Type_Scale <- ggplot(Ten_Years_Sales, aes(x = Six_Month_Period_Mar_Sep, y = Median_Price, group = Type, colour = Type)) +
  geom_line(size = 1.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        legend.title = element_blank(), 
        legend.position = "right", 
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "Inner City Units Show Early Signs of Price Growth",
       x = "Six Month Period", 
       y = " Median Price", 
       caption = "Median Price by Property Type and Complex Size by Six Month Periods") +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  scale_colour_manual(labels = legend_names, values = line_colours))
```

In a sign of the market returning to positive growth, both townhouse categories as well as mid-rise apartment buildings showed median price increases during the past six month period ending September 2018. High-rise apartment building median prices have been relatively flat over the past 18 months. 

At the end of the September 2018 six month period, Medium Sized Townhouse Complexes had the highest median price of $578,750 recording a growth rate of 3.1% per annum over the past 10 years. This is followed by Small Size Townhouse complexes which recorded a median price of $546,000 for the same period at a growth rate of 2% per annum over the past 10 years. High Rise, Mid Rise and Low Rise Apartment Buildings recorded median prices of $500,000, $475,250 and $395,000 during the September 2018 six month period at growth rates of 1.3%, 1.7% and 1.2% per annum over the past 10 years respectively.

```{r Median Price Animation Graph, eval=FALSE, fig.align="centre", fig.height=7, fig.length=12, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

Property_Type_Scale2 <- ggplot(Ten_Years_Sales, aes(x = Six_Month_Period_Mar_Sep, y = Median_Price, 
                                                    group = Type, colour = Type, frame = Six_Month_Period_Mar_Sep)) +
  geom_point(size = 4) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        legend.title = element_blank(), 
        legend.position = "none",
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "Inner City Unit Median Price Movements",
       x = NULL, 
       y = " Median Price", 
       caption = "Median Price by Property Type and Complex Size by Six Month Periods") +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
   scale_colour_manual(labels = legend_names, values = line_colours)

ggplotly(Property_Type_Scale2, tooltip = "Median_Price", width = 2) 

```

## SALES VOLUMES BY CATEGORY

The following chart displays the number of sales by category as a proportion of total sales per six month period. The Inner Brisbane unit market peaked in sales volumes during the height of the apartment boom in 2015. However, there were only material increases in sales volumes proportions in high-rise apartment buildings and to a lesser extent, mid-rise apartment buildings. Following initial steep declines in sales numbers beginning in 2016, the proportional drop in sales from period to period is now minimal with sales volumes sitting at levels seen just prior to the apartment boom and signifying a stabilising market.

```{r Number of Sales Bar Chart, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "centre", fig.width = 10, height = 6}

ggplot(data = Ten_Years_Sales, aes(x = Six_Month_Period_Mar_Sep, y = No_Sales, group = Type, fill = Type)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(labels = legend_names, values = line_colours) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "right",
        legend.title = element_blank()) +
  labs(title = "The Largest Reduction in Sales Volumes Has Been in Large Scale Apartment Buildings",
       x = "Six Month Period",
       y = "Number of Sales",
       caption = "Number of Sales by Property Type and Complex Size by Six Month Periods") +
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE)) 
   

```

During the last six month period ending September 2018, high-rise apartments recorded the most sales with 1,065, followed by mid-rise apartment buildings with 328 and low-rise apartments with 311. Small size townhouse complexes recorded 141 sales with a further 48 townhouse sales in medium sized townhouse complexes.

From their respective peaks, high-rise apartment sales volumes have fallen -68.9%, mid-rise apartments have fallen by 56.1% and low-rise apartments by -45.1%. Small size townhouse complexe's sales volumes similarly declined by -44.8%, whilst townhouse sales in medium sized complexes declined by -28.4%. 

## CAPITAL GROWTH

Place Advisory has also analysed the annual capital growth rates achieved on all resales from the past **12 months** ending September 2018. These are plotted on the map of Brisbane below, giving you a better visual of what is happening in the Inner Brisbane unit market. 

*This map is interactive, scroll around and use the filter tab in the top right corner.*
```{r Leaflet of Capital Growth, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "centre"}

# create 1 year of sales data
One_Years_Sales_Data <- sales_data_merge %>%
  filter(Six_Month_Period_Mar_Sep > "2017 September" & Six_Month_Period_Mar_Sep < "2019 March") %>%
  mutate(Type = paste(Property_Type, " ",  Scale)) 

# merge ressale data
resale_merge <- left_join(One_Years_Sales_Data, resales_cleaned, by = c("Entry_ID" = "Entry_ID"))

# remove new rows and those with no capital growth recorded becuase of a holding period below 1 year
resale_merge <- resale_merge %>%
  filter(!is.na(`Holding Period`)) %>%
  filter(!is.na(`Annual Capital Growth`)) %>%
  filter(Type != "Townhouses Large scale (41 units or greater)")

# break sales data into 6 bins

# less than 0%

under_zero <- resale_merge %>%
  filter(`Annual Capital Growth` < 0)

zero_twohalf <- resale_merge %>%
  filter(`Annual Capital Growth` > 0 & `Annual Capital Growth` <= 0.025)

twohalf_five <- resale_merge %>%
  filter(`Annual Capital Growth` > 0.025 & `Annual Capital Growth` <= 0.05)

five_sevenhalf <- resale_merge %>%
  filter(`Annual Capital Growth` > 0.05 & `Annual Capital Growth` <= 0.075)

sevenhalf_plus <- resale_merge %>%
  filter(`Annual Capital Growth` > 0.075) 

# Create leaflet map

Brisbane_Map2 <- leaflet(options = leafletOptions(dragging = TRUE, minZoom = 12)) %>%
  setMaxBounds(lng1 = 152.970951, lng2 = 153.116971, lat1 = -27.410852, lat2 = -27.532954) %>%
  addProviderTiles("Esri") %>% 
  addCircleMarkers(data = under_zero, lng = ~Longitude, lat = ~Latitude, radius = 1.5, color = "darkred", fillOpacity = 0.5, group = "Less than 0% Per Annum") %>% 
  addCircleMarkers(data = zero_twohalf, lng = ~Longitude, lat = ~Latitude, radius = 1, color = "orangered", fillOpacity = 0.5, group = "Between 0% and 2.5% Per Annum") %>%
  addCircleMarkers(data = twohalf_five, lng = ~Longitude, lat = ~Latitude, radius = 1, color = "orange", fillOpacity = 0.5, group = "Between 2.5% and 5% Per Annum") %>%
  addCircleMarkers(data = five_sevenhalf, lng = ~Longitude, lat = ~Latitude, radius = 1, color = "darkseagreen", fillOpacity = 0.5, group = "Between 5% and 7.5% Per Annum") %>%
  addCircleMarkers(data = sevenhalf_plus, lng = ~Longitude, lat = ~Latitude, radius = 1, color = "darkgreen", fillOpacity = 0.5, group = "More than 7.5% Per Annum") %>%
   addPolygons(data = myCircles1, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "1km Ring") %>%
   addPolygons(data = myCircles2, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "2km Ring") %>%
   addPolygons(data = myCircles3, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "3km Ring") %>%
   addPolygons(data = myCircles4, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "4km Ring") %>%
   addPolygons(data = myCircles5, lng = ~lon, lat = ~lat, color = "black", fillOpacity = 0, group = "5km Ring") %>%
 addLayersControl(overlayGroups = c("Less than 0% Per Annum", "Between 0% and 2.5% Per Annum", "Between 2.5% and 5% Per Annum", "Between 5% and 7.5% Per Annum", "More than 7.5% Per Annum", "1km Ring", "2km Ring", "3km Ring", "4km Ring", "5km Ring"))

Brisbane_Map2
```

The map shows that despite losses having occurred throughout Inner Brisbane with no one particular location in focus, the stronger gains above 5% per annum have been predominantly achieved in the suburbs of New Farm and Teneriffe. These two suburbs are consistently two of Brisbane's most expensive and best performing due their prime location within 3km of the Brisbane CBD and along the Brisbane River with a popular park and river walk, an abundance of restaurants and entertainment options.

## DISPERSION OF CAPITAL GROWTH

The following graph analysies the spread of annual capital growth rates that were achieved on unit resales throughout Inner Brisbane over the last 12 months ending September 2018. Red bars indicate a negative growth rate while green bars indicate a positive growth rate. While the market is emerging from a period of weakness, gains still far outweigh losses. 
```{r Density Histogram of capital growth, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "centre", height = 10}

# create conditional fill column
resale_merge$positive_growth <- ifelse(resale_merge$`Annual Capital Growth` > 0, "Positive Growth", "Negative Growth")

# Create density histogram

ggplot(resale_merge, aes(`Annual Capital Growth` * 100, fill = positive_growth)) +
  geom_histogram(binwidth = 1, colour = "black", aplha = 0.5, position = position_dodge(width = 2)) +
  scale_fill_manual(values = c("darkred", "darkgreen")) +
  xlim(-15, 15) +
  geom_vline(xintercept = 0, size = 1, colour = "black") +
  geom_vline(xintercept = 5, size = 1, colour = "black") +
  geom_vline(xintercept = -5, size = 1, colour = "black") +
   theme(legend.title = element_blank(), 
        legend.position = "right",
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(x = "Average Annual Capital Growth (%)",
       y = "Number of Sales",
       title = "Recorded Growth Rate on Reslaes",
       caption = " Average Annual Growth of Result Units: 12 Months to September 2018") 
 

```

As can be seen in the graph, the majority of resales recorded an annual growth rate of between -5% to 5% per annum. Positively, unit resales have recorded more positive growth rates than negative growth rates. Overall, of resales during the 12 month period to September 2018 recorded positive growth. To read our past report on Brisbane's best performing suburbs [click here](http://www.placeprojects.com.au/brisbanes-best-performing-suburbs-2/)

After analysing the Inner Brisbane unit market by breaking it down into five different categories, Place Advisory has revealed that after recent weakness, the Inner Brisbane market is showing signs of a stabilising market and early signs returning to positive growth. This comes as no surprise when considering strong and increasing population growth, an improving economy and a sharp reduction in new unit supply to the region as outlined in our [previous reports](http://www.placeprojects.com.au/research/). Despite stricter lending conditions in the current economic environment, the future potential for price growth remains strong for Brisbane.

&nbsp; 
&nbsp; 
&nbsp; 
&nbsp; 
&nbsp; 















