---
title: "Place Projects Monthly Meeting November 2018"
author: "Jay Blake - Place Projects"
date: "November 19, 2018"
output: slidy_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(plotly)
library(dygraphs)
library(forecast)
library(tidyr)

```


## QLD Population Growth Rate Continues to Increase

```{r QLD Population, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align='center'}

# Load population data
population_data <- read.csv("R:/Projects/Jay/Jay Portfolio/R Projects/Monthly Meeting Files/Monthly Meeting November 2018/population data abs.csv")


# Format date variable
population_data_clean <- population_data %>%
  mutate(Quarterly.Period = as.Date(Quarterly.Period, format = "%d-%b-%y"))

# Spread data to extract vector of values
population_data_spread <- spread(population_data_clean, Type.of.Increase, Net.Increase)

# Impute values that went to different column in the right spot
population_data_spread[36,4] = 6231
population_data_spread[37,4] = 9001

# extract values for into vectors for time series data
Natural_Increase <- population_data_spread$`Natural increase`
Interstate_Migration <- population_data_spread$`Interstate Migration`
overseas_Migration <- population_data_spread$`Overseas Migration`

# Combine vectors

QLD_Population_Timeseries <- cbind(Natural_Increase, Interstate_Migration, overseas_Migration)
 
# Convert data to time series
QLD_Population_Timeseries <- ts(QLD_Population_Timeseries, start = c(2009, 1), end = c(2018, 1), frequency = 4)

# Plot data on time series graph
dygraph(QLD_Population_Timeseries, "Population Growth Rate to Queensland Increases Into 2018") %>%
  dyStackedBarGroup(c('overseas_Migration', 'Interstate_Migration', 'Natural_Increase')) %>% # Add order of Stacked Bars
  dyRangeSelector() %>% # Add Range Selector
  dyAxis("y", label = "Net Population Increase") # Label of y-axis


```


## New Supply to the Brisbane Market is Drying Up


```{r Brisbane New Apartment Supply, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align='center'}

# Load data
left_data <- read.csv("R:/Projects/Jay/Jay Portfolio/R Projects/Monthly Meeting Files/Monthly Meeting November 2018/Apartment Report Left To Complete.csv")

# Clean data
left_data_clean <- left_data %>%
  mutate(Left_To._Complete = as.integer(gsub("[%]", "", Left_To._Complete)))

# Make plot
ggplotly(ggplot(data = left_data_clean, mapping = aes(x = Period, y = Left_To._Complete, fill = Left_To._Complete)) +
  geom_bar(stat = "identity") +
  labs(title = "Soon All Current New Apartment Supply WIll Complete Construction",
       y = "Percentage Left to Complete Construction", 
       x = "Year End") +
  guides(fill = FALSE) +
  theme_bw()) 
```

 - Little New Supply Coming
 - Approximately 80% of current new supply purchased
 - 8% DA Submissions are New Applications
 - 60% of DA Submissions are Deferred or Abandoned

## Brisbane Rental Vacancy Is Declining

```{r Brisbane Vacancy Rate, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align='center'}

# Load vacancy data
rental_vacancy_data <- read.csv("R:/Projects/Jay/Jay Portfolio/R Projects/Monthly Meeting Files/Monthly Meeting November 2018/Vacancy Rate Data Base REIQ.csv")


# Change names of variable

names(rental_vacancy_data) <- c("Period", "Greater.Brisbane", "Brisbane.LGA", "Inner..0.5km.", "Middle..5.20km.", "Outer.Brisban")

# Clean and modify data
rental_vacancy_data_clean <- rental_vacancy_data %>%
  mutate(GB = as.numeric(gsub("[%]", "", Greater.Brisbane))) %>%
  mutate(BLGA = as.numeric(gsub("[%]", "", Brisbane.LGA))) %>%
  mutate(IB = as.numeric(gsub("[%]", "", Inner..0.5km.))) %>%
  mutate(MB = as.numeric(gsub("[%]", "", Middle..5.20km.))) %>%
  mutate(OB = as.numeric(gsub("[%]", "", Outer.Brisban))) %>%
  mutate(Period = as.ordered(Period)) %>%
  select(1,7:11)

# Adjust ordered levels of period
levels(rental_vacancy_data_clean) <- c("Jun-08", "Sep-08", "Mar-09",  "Sep-09", "Mar-10", "Sep-10", "Mar-11", "Jun-11", "Sep-11", "Dec-11", "Mar-12", "Jun-12", "Sep-12", "Dec-12", "Mar-13", "Jun-13", "Sep-13", "Dec-13", "Mar-14", "Jun-14", "Sep-14", "Dec-14", "Mar-15", "Jun-15", "Sep-15", "Dec-15", "Mar-16", "Jun-16", "Sep-16",  "Dec-16", "Mar-17", "Jun-17", "Sep-17", "Dec-17", "Mar-18", "Jun-18", "Sep-18") 

# Extract values for time series data Brisbane LGA
BrisbaneLGA <- rental_vacancy_data_clean$BLGA[17:37]

# Extract values for time series data Inner Brisbane
Inner_Brisbane <- rental_vacancy_data_clean$IB[17:37]

# Join vectors of data
Brisbane_Vacancy_Timeseries <- cbind(BrisbaneLGA, Inner_Brisbane)
 
# Convert data to time series
Brisbane_Vacancy_Timeseries <- ts(Brisbane_Vacancy_Timeseries, start = c(2013, 3), end = c(2018, 3), frequency = 4)

# Plot time series graph
dygraph(Brisbane_Vacancy_Timeseries, main = "Brisbane Vacancy is Tightening") %>%
  dyRangeSelector() %>% # insert range selector
  dyShading(from="2017-9-30", to="2018-9-30", color="#CCEBD6") %>% # Shading
  dyAxis("y", label = "Vacancy Rate (%)", valueRange = c(0, 5)) # Label and range of y-axis



```

## Rental Prices Increasing Again As Vacancy Rate Falls and Supply Dries Up

```{r Inner Brisbane Apartment Retal Prices, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align='center'}

# Load rental price data
rental_data <- read.csv("R:/Projects/Jay/Jay Portfolio/R Projects/Monthly Meeting Files/Monthly Meeting November 2018/rental prices Inner Brisbane Apartments.csv")

rental_data_clean <- rental_data %>%
  mutate(Rent = as.integer(gsub("[$]", "", Apartment.Weekly.Rental.Price))) %>%
  select(1,3)

ggplotly(ggplot(rental_data_clean, aes(x = Year, y = Rent)) +
  geom_line(stat = "identity", lwd = 2, color = "red") + 
  labs(title = "Apartment Rental Prices Rebound in 2018",
       y = "Average Weekly Asking Rent ($)", 
       x = "Year") +
  guides(fill = FALSE) +
  scale_colour_manual(values = "red"))
 

```

## Whats Ahead in the Next Few Years?

- Demand is now outstripping demand
- supply to continue to be absorbed in 2019
- Rental prices to begin to rise more quickly
- With better rental returns and more competitive rental market more will look to buy
- Sales volumes will increase
- With the increased demand to buy a property prices will rise

## Questions?